Distributions

### 2022-01-10 Ch2_distributions/Ch2_Figures.Rmd
Not knitting to word.
Saving tables as csv files.

---
title: "Distributions"
author: "Javiera Rudolph"
output:
  word_document:
    toc: yes
  html_document:
    toc: yes
---

@@

Table 1 - BIC values obtained for models fitted to velocity data across pooling levels. Probability density functions considered included the Gamma, Weibull, and Lognormal distributions. Multi distribution models selected the best fitting distribution model for each family group or individual, allowing for variation not only in estimated parameters, but also in the distribution used. Based on BIC values, the best fitting model is the Multi-distribution with Partial Pooling, closely followed by the Complete Pooling Lognormal model.

@@

BIC_table

@@

#library(gt)

@@

gt_tbl %>% 
  tab_header(
    title = md("**Model comparisons across levels**")
  ) %>% 
  tab_stubhead(label = "Model") %>% 
  tab_row_group(
    group = "NP",
    rows = 8:11
  ) %>% 
  tab_row_group(
    group = "PP",
    rows = 4:7
  ) %>% 
  tab_row_group(
    group = "CP", 
    rows = 1:3
  ) %>% 
  tab_spanner(
    label = md("**BIC**"),
    columns = vars(BIC, deltaBIC_withinmodels, deltaBIC_acrossmodels)
  ) %>% 
  cols_label(
    deltaBIC_withinmodels = html("&Delta; BIC<sub>within</sub>"),
    deltaBIC_acrossmodels = html("&Delta; BIC<sub>across</sub>"),
  )

# -> gt_table_bic
#   
# gtsave(gt_table_bic, "Ch2_distributions/aic_bic_table.png") 
```

@@

cp.bic %>% 
  bind_rows(pp.bic) %>% 
  bind_rows(np.bic) %>% 
  filter(., deltaBIC != 0) %>% 
  mutate(model = factor(model, levels = c("CP", "PP", "NP"))) %>% 
  group_by(model, boot) %>% 
  summarise(min = min(deltaBIC)) %>% 
  group_by(model) %>% 
  summarise(minimum = min(min),
            median = median(min),
            mean = mean(min),
            q2.5 = quantile(min, probs = 0.025),
            q97.5 = quantile(min, probs = 0.975))

>>>>

---
title: "Distributions"
author: "Javiera Rudolph"
output:
  html_document:
    toc: yes
---

@@

Table 1 - BIC values obtained for models fitted to velocity data across pooling levels. Probability density functions considered included the Gamma, Weibull, and Lognormal distributions. Multi distribution models selected the best fitting distribution model for each social group or individual, allowing for variation not only in estimated parameters, but also in the distribution used. Based on BIC values, the best fitting model is the Multi-distribution with Partial Pooling, followed by the Lognormal PP, and Lognormal CP.

@@

BIC_table
write.csv(BIC_table, file = "Ch2_distributions/Figures/bic_table.csv")

@@

library(gt)

@@

gt_tbl %>% 
  tab_header(
    title = md("**Model comparisons across levels**")
  ) %>% 
  tab_stubhead(label = "Model") %>% 
  tab_row_group(
    group = "NP",
    rows = 8:11
  ) %>% 
  tab_row_group(
    group = "PP",
    rows = 4:7
  ) %>% 
  tab_row_group(
    group = "CP", 
    rows = 1:3
  ) %>% 
  tab_spanner(
    label = md("**BIC**"),
    columns = vars(BIC, deltaBIC_withinmodels, deltaBIC_acrossmodels)
  ) %>% 
  cols_label(
    deltaBIC_withinmodels = html("&Delta; BIC<sub>within</sub>"),
    deltaBIC_acrossmodels = html("&Delta; BIC<sub>across</sub>"),
  ) -> gt_table_bic

gtsave(gt_table_bic, "Ch2_distributions/Figures/bic_table.png")
```

@@

cp.bic %>% 
  bind_rows(pp.bic) %>% 
  bind_rows(np.bic) %>% 
  filter(., deltaBIC != 0) %>% 
  mutate(model = factor(model, levels = c("CP", "PP", "NP"))) %>% 
  group_by(model, boot) %>% 
  summarise(min = min(deltaBIC)) %>% 
  group_by(model) %>% 
  summarise(minimum = min(min),
            median = median(min),
            mean = mean(min),
            q2.5 = quantile(min, probs = 0.025),
            q97.5 = quantile(min, probs = 0.975)) -> bic_2nd

bic_2nd

write.csv(bic_2nd, file = "Ch2_distributions/Figures/bic_2nd.csv")
